Phase paper outline

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
update outline Jess

\subsection*{Time-averaged phase}

@@

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item BP and Heart rate
	\begin{itemize}
	\item phase lag between changes in heart rate and changes in BP
	\end{itemize}
\item Something about SCG or ECG
\item cerebral blood flow
\end{itemize}

@@

>>>>

\subsection*{Time-averaged phase, or Frequency domain phase}

@@

\section*{When each method can fail}
\begin{itemize}
\item Frequency domain phase difference can fail when one oscillation leads another by more than half of a cycle.
\item Time-domain phase is only accessible at one frequency at a time if the Hilbert transform is used
\item Time-domain phase must have \textit{some} problems if wavelet 
\end{itemize}

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item BP and Heart rate
	\begin{itemize}
	\item phase lag between changes in heart rate and changes in BP
	\end{itemize}
\item Something about SCG or ECG
\item cerebral blood flow
\item JESS
\end{itemize}

@@

\section*{Results}

	\subsection*{Figures}
	\begin{enumerate}
	\item Simulation
		\begin{enumerate}
		\item Time series of raw simulated data + added noise
		\item Power spectrum of the data
		\item Time-domain phase 
		\item Accuracy of each detector at a range of signal to noise ratios
		\end{enumerate}
	\item Rat data
		\begin{enumerate}
		\item BP and cortical perfusion
		\item Phase interactions between two or three regions on the renal surface
		\end{enumerate}
	\item{Human data}
		\begin{enumerate}
		\item BP and heart rate
		\item Use phase to find the lag between a change in bp and a change in heart rate
		\end{}
	\end{enumerate}
